\TheTitle

### 2015-08-17 linvis.tex
Discussion: Future Work:
We discuss the differences in our tool versus the other tool, providing a
side-by-side view of the visualization models used by our tool and gitk. We
show what information can be gathered quickly and effectively through the use
of our tool that cannot be gathered as effectively with gitk.

There is still a lot of work to be done in the future work section. We need to
talk about how our tool does not provide the diffs, though we have that
information and could very easily display it. Furthermore, we could use the
diff to determine what lines were changed, which lines we

\ifdraft
	\documentclass[conference, draftclsnofoot]{IEEEtran}
	\def\baselinestretch{1}
	\setlength{\marginparwidth}{2cm}
\else
	\documentclass[conferece, final]{IEEEtran}
\fi

@@

	With an average of over 900 top-level merges into the Linux kernel per
	release, some containing thousands of commits, many containing hundreds
	of commits, maintenance of older versions of the kernel becomes nearly
	impossible. For security, performance, and changing hardware,
	maintainers must understand the changes made to current versions of the
	kernel, and show these changes fit into older versions in order to make
	the necessary merges and modifications to the older versions. Current
	tools provide information about repositories through the directed
	acyclic graph (DAG) which is helpful for smaller projects, but with the
	scale and number of branches in the kernel, the DAG becomes
	overwhelming very quickly.

@@

\section{Future Work}
We have limited search functionality regarding actual files involved in
commits. If a user knows which file they are working with and what has changed
in a given file, they are unable to look specifically for commits pertaining to
that file. Adding a search filter for searching by file would allow maintainers
to perform this search.

@@

At this time, we have no evidence that our tool is able to improve the
work-flow of maintainers. We believe that the tool is able to improve the
work-flow and performance of maintainers because it is able to better assist
users because it provides cleaner mechanisms of working with the data. It is
able to provide more relevant information, while removing information that is
irrelevant to a given module or set of merges.

>>>>

\ifdraft
	\documentclass[conference, draftclsnofoot]{IEEEtran}
	\def\baselinestretch{1}
	\setlength{\marginparwidth}{2cm}
\else
        \documentclass[conference]{IEEEtran}
	\def\baselinestretch{1}
	\setlength{\marginparwidth}{2cm}

	% \documentclass[conferece, final]{IEEEtran}
\fi

@@

	With an average of over 900 top-level merges into the Linux kernel per
	release, some containing thousands of commits, many containing hundreds
	of commits, maintenance of older versions of the kernel becomes nearly
	impossible. For security, performance, and changing hardware needs,
	maintainers must understand the changes made to current versions of the
	kernel, and understand how these changes fit into older version in
        order to make the necessary merges and modifications to the older
        versions. Current tools provide information about repositories through
        the directed acyclic graph (DAG) which is helpful for smaller projects,
        but with the scale and number of branches in the kernel, the DAG
        becomes overwhelming very quickly.

@@

\section{Discussion}

Our tool provides mechanisms and visualizations that other tools are unable to
produce. Continuous mining of the repository provides an additional dimension
to the dataset that would otherwise be lost, enabling us to reliably build
trees from the information we have.

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/042dd_DAG.png}
	\caption{Merge Dag View}
	\label{fig:dag_view}
\end{figure}

\begin{figure}[h]
	\centering
	\includegraphics[width=0.47\textwidth]{figures/042dd_tree.png}
	\caption{Merge Tree View}
	\label{fig:tree_view}
\end{figure}

Our goal was to build a tool to enable maintainers to effectively navigate and
pull explanation of the changes performed to the kernel over a release.
Achieving this goal includes removing information that does not pertain to given
users. In figure \ref{fig:dag_view} and figure \ref{fig:tree_view}, we can
visually compare the results returned from gitk and our tool for the top-level
merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6'' from kernel version 3.10.
The relevant information in both of these figures is identical, but the
presentation durastically changes our understanding of what we are seeing.

This merge is relatively small, containing only four merges, three of which
only contain a single commit, and the last containing two commits. With our
tool, we are able to immediately see what commits and merges pertain to our
section of the kernel. The DAG view of this provides almost no explanation,
futhermore, users must work to determine where this merge ends and the next one
begins.

Our tool further enhances our understanding by immediately giving us the files
that were edited and the modules. We are able to determine that three files,
``palamas-regulator.c'' had two lines added and two lines removed,
``dbx500-prcmu.c'' had 12 lines added and 12 lines removed, and ``core.c'' had
5 lines added and 2 lines removed in the merge. Finally, we are able to
determine that only the module ``regulator'' was modified in this merge, and
there were 5 commits in the merge to this module.

\subsection{Performance Evaluation}

Re-structuring the kernel into a tree changes the runtime for the structures.
Originally, we were performing all of our tree-navigation using recursive SQL
queries. Recursive queries have terrible performance, with the average response
time from the database being around 3 seconds for a single operation. We found
that it was far more time-efficient to load an entire tree directly into
memory, then iterate over the objects returned to build the tree structures,
than it was to have the dbms perform the tree traversals, building the specific
trees for a commit. At this time, we have re-implemented the breadcrumbs, the
files, and the main tree to enhance the response times. We will discuss some We
will discuss the changes made.

The breadcrumbs are generated at response
time, so they must be generated quickly. We began with a single recursive SQL
query, but was unable get the results in the required time, causing all result
pages to render slowly. We replaced the recursive query with a single query
that would grab the entire merge tree, rooted at the top-level merge.

The items returned from the database contained the commit id, the commit id of
the merge with the Linux kernel, and the next merge in the path to the
top-level merge.

We placed each item in the results into a dictionary using the commit id as the
key. Using the following method, we build the dictionary into a list of commit
IDs for the breadcrumbs.

\begin{verbatim}
current = cid
breadcrumbs = [cid]
while current is not top-level merge:
        breadcrumbs.append(current.next)
return reverse(breacrumbs)
\end{verbatim}

This maintains the O(n) runtime for generating the breadcrumbs, while using an
iterative method for traversing the tree.

We use similar methods to generate the file information and the tree. Both are
generated asynchronously, allowing us to use spinners to help improve the user
experience. We are using AJAX requests to generate the asynchronous requests,
are are having very good results.

\subsection{Extendability}
Due to how the asynchronous requests are performed, it is possible to query the
server for the tree and file information directly, allowing other users to
build their own front-ends for working with our tree-based system.

The tree and file information is accessible through
http://li.turingmachine.org/data/tree/JSON/<commit id> and
http://li.turingmachine.org/data/files/JSON/<commit id>, respectively.
The tree is generated as many nested javascript objects. The tree response does
not contain any notion of the current commit and will only return the entire
merge tree.

The tree responses are generated as a single object. This object is the root
node of the tree, and may contain many objects with the same fields in the
``children'' field. The full response format for the tree looks like:

\begin{itemize}
        \item ``cid'': string, commit id
        \item ``name'': string, One-line log preview
        \item ``author'': string, Author's name
        \item ``mlinus'': string, commit id of top-level merge
        \item ``mnext'': string, commit id of the next merge on path to
                top-level
        \item ``children'': list, list of items with the same fields. Null if
                no children
\end{itemize}

The file responses contain only the files that the current merge or commit
works with. The response is a single object in the form of a tree. This object
is the root of the tree, and represents the current merge or commit. If the
current position in the tree is an inner node, the response will contain the
children in the ``children'' field, otherwise ``children'' will be null. The
full response format for the file response looks like:

\begin{itemize}
        \item ``cid'': string, commit id
        \item ``files'': list, list of tulples in the format
                \begin{enumerate}
                        \item Filename: string
                        \item Lines added: unsigned integer
                        \item Lines removed: unsigned integer
                \end{enumerate}
        \item ``mnext'': string, the commit id of the next merge toward the
                top-level merge
        \item ``children'': list, List of all child objects with the same
                fields. Null if no children.
\end{itemize}

\section{Future Work}

This project was implemented over the course of 4 months, interleaved with
other course projects and assignments. There are still many areas that could
use improvements before the full potential of our model can be reached and
understood with our tool. Here, we outline various areas that still need more
attention.

\subsection{Files}
We have limited functionality surrounding files, for both search and presented
information.

\evantodo{User cases integrated into files}

% There is currently no functionality surrounding searching for a given file.
% Users who know what file they are working with
%
% We have limited search functionality regarding actual files involved in
% commits. If a user knows which file they are working with and what has changed
% in a given file, they are unable to look specifically for commits pertaining to
% that file. Adding a search filter for searching by file would allow maintainers
% to perform this search.

\subsection{Testing}
At this time, we have no evidence that our tool is able to improve the
work-flow of maintainers. We believe that the tool is able to improve the
work-flow and performance of maintainers because it is able to better assist
users because it provides cleaner mechanisms of working with the data. It is
able to provide more relevant information, while removing information that is
irrelevant to a given module or set of merges.

We could perform user-testing, or have some example cases where the tool is
used and the users provide feedback on how it improves or hurts their work
flow.

@@
